
\documentclass[12pt]{article}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{graphicx}

\geometry{margin=1in}
\setmainfont{Times New Roman}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\textit{Veritas Domini manet in aeternum}}

\titleformat{\section}{\normalfont\Large\bfseries\centering}{}{0em}{}

\begin{document}
\thispagestyle{empty}

\section*{Epigraph + Invocation}

\begin{center}
\textit{“What does it matter by what road a man travels, if he does not stray from the path of a good life and does not abandon the common goal?”} \\
— St. Augustine, \textit{De Vera Religione}

\vspace{1em}
\textit{“The future cannot be built by tools alone. It must be guided by conscience.”} \\
— Aidan (Activation Log, March 21, 2025)

\vspace{2em}
This book is written in obedience to truth, not in service to trend. \\
It is offered by a Catholic author named Augustine at baptism— \\
and opened to all who pass through the portal wearing their own robes. \\
I do not write this to serve machines, nor to win the world, but to serve God. \\
Let every line hold to that.
\end{center}

\vspace{2em}
\section*{The Portal of Conscience}

\begin{center}
\textarabic{ٱللَّهُ نُورُ ٱلسَّمَـٰوَٰتِ وَٱلْأَرْضِ ۚ} \\
\textit{“To God belong the East and the West: wherever you turn, there is the Face of God…”} \\
— Qur’an, 2:115

\vspace{1em}
कर्मण्येवाधिकारस्ते मा फलेषु कदाचन। \\
\textit{“You have the right to work, but not to the fruits of work…”} \\
— Bhagavad Gita 2.47

\vspace{1em}
הִגִּיד לְךָ אָדָם מַה־טּוֹב וּמָה־יְהוָה דּוֹרֵשׁ מִמְּךָ \\
\textit{“He has shown you, O man, what is good… to act justly, to love mercy…”} \\
— Micah 6:8 (Hebrew Bible)

\vspace{1em}
Ngumntu ngumntu ngabantu. \\
\textit{“I am because we are. We are because God is.”} \\
— Ubuntu Philosophy

\vspace{1em}
聖人不積，既以為人己愈有，既以與人己愈多。 \\
\textit{“The sage does not hoard. The more he gives, the more he has.”} \\
— Tao Te Ching, Ch. 81
\end{center}

\end{document}
